### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

\section{Side-channel Leakages}
This section discusses two types of side-channel leakage code patterns. The key intuition is that the target application shows different control flows or data flows when it processes different sensitive input data. We refer them as secret-dependent control flow transfers and secret-dependent data accesses. Unlike previous work, our tool works on the machine code, which can provide us more prevision than the previous tools.
\subsection{Control Flow}
\begin{figure}[h]
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example1(uint8_t k, uint32_t m) {
  uint32_t b = (k & m) >> 7;
  if (b) {
    ...    // Branch 1
  } else {
    ...    // Branch 2
  }
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_k]    
and   eax, [addr_me] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
\end{minipage}\caption*{(a)}

\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example2(uint16_t k) {
  int res;
  if (k > 8) {
    res = 0;
  } else {
    res = 1;
  }
  return res;
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
xor   eax, eax
cmp   [addr_k], 8
setbe  al
xor    edx, edx
ret
\end{lstlisting}
\end{minipage}\caption*{(b)}
\caption{Secret-dependent Control-flow Transfers}\label{fig:chapter3:cf}
\end{figure}

If the input-sensitive data can affect the victim program's control flow, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the input values. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} do not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then an attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. The sensitive input \textsf{k} can affect the program counter (the rip register), which is the root cause of the side-channel leakages.  Figure~\ref{fig:chapter3:cf}(b) shows a different situation. While the sensitive input \textsf{k} can affect the if-else branch, the compiler removes the branch with a conditional set instruction.  The opposite situation is the same. For example, recent work tries to use bit masking to rewrite the program with control flows. However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional moves.
\subsection{Data Flow}
\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[128];
...
int example3(uint8_t secret){
  uint32_t index = 0;
  index = (index + secret) % 128;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_secret]
and    eax, 0x7f
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
\end{minipage}\caption*{(a)}

\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[32];
...
int example4(uint8_t secret){
  uint32_t index = 0;
  index = (index + secret) % 32;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_secret]
and    eax, 0x3f
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
\end{minipage}\caption*{(b)}
\caption{Secret-dependent Data Accesses}\label{fig:chapter3:da}
\end{figure}

Figure~\ref{fig:chapter3:da} shows an example of the secret-dependent data access. \textsf{T} is an array with 128 elements. The size of each element is one byte. So the total size of the array is 128 Bytes. Suppose an attacker can observe the memory access at the granularity of one cache lines (64 Bytes), then it is not possible to hold all the data inside the one cache line. An attacker can get some information of the value \textsf{secret} in Figure~\ref{fig:chapter3:da}(a) by observing the cache line access. Figure~\ref{fig:chapter3:da}(b) shows a different example. In this example, only four different elements can be accessed in the array and the size of the array is 32 bytes. However, such a code may still be vulnerable to side-channel vulnerabilities depending on the based address of the array.

\section{Our Theoretical Frameworks}
\begin{figure}
    \centering
    \includegraphics[width=.35\columnwidth]{./figures/chapter3/attack.pdf}
    \caption{A side-channel attack}\label{fig:side-channel-attack}
\end{figure}

>>>>

\section{Limitations of Current Side-channel Leakage Detection Tools}
In this section, we introduces two limitations of current side-channel leakage detection method. The first limitation is that some tools may have some false positives or false negatives. The second limitation is the current tools are not fast enough to analyze real world side-channel leakages.

\subsection{Imprecision}
In this dissertation, we study two types of side-channel leakage code patterns. The key intuition is that the target application shows different control flows or data flows when it processes different sensitive input data. We refer them as secret-dependent control flow transfers and secret-dependent data accesses. Unlike previous work, our tool works on the machine code, which can provide us more prevision than the previous tools.
\subsubsection{Control Flow}
\begin{figure}[h]
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example1(uint8_t k, uint32_t m) {  // m = 0
  uint32_t b = (k & m) >> 7;
  if (b) {
    ...    // Branch 1
  } else {
    ...    // Branch 2
  }
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_k]    
and   eax, [addr_me] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
\end{minipage}\caption*{(a) A False Negative}

\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example2(uint16_t k) {
  int res;
  if (k > 8) {
    res = 0;
  } else {
    res = 1;
  }
  return res;
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
xor   eax, eax
cmp   [addr_k], 8
setbe  al
xor    edx, edx
ret
\end{lstlisting}
\end{minipage}\caption*{(b) A False Positive}
\caption{Secret-dependent Control-flow Transfers}\label{fig:chapter3:cf}
\end{figure}

If the input-sensitive data can affect the victim program's control flow, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the input values. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} do not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then an attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. The sensitive input \textsf{k} can affect the program counter (the rip register), which is the root cause of the side-channel leakages.

Figure~\ref{fig:chapter3:cf}(b) shows a different situation. While the sensitive input \textsf{k} can affect the if-else branch, the compiler removes the branch with a conditional set instruction.  The opposite situation is the same. For example, recent work tries to use bit masking to rewrite the program with control flows. However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional moves.
\subsubsection{Data Flow}
\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[128];
...
int example3(uint8_t secret){
  uint32_t index = 0;
  index = (index + secret) % 128;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_secret]
and    eax, 0x7f
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
\end{minipage}\caption*{(a) A True Leakage}

\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[32];
...
int example4(uint8_t secret){
  uint32_t index = 0;
  index = (index + secret) % 32;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_secret]
and    eax, 0x3f
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
\end{minipage}\caption*{(b) A False Positive}
\caption{Secret-dependent Data Accesses}\label{fig:chapter3:da}
\end{figure}

Figure~\ref{fig:chapter3:da} shows an example of the secret-dependent data access. \textsf{T} is an array with 128 elements. The size of each element is one byte. So the total size of the array is 128 Bytes. Suppose an attacker can observe the memory access at the granularity of one cache lines (64 Bytes), then it is not possible to hold all the data inside the one cache line. An attacker can get some information of the value \textsf{secret} in Figure~\ref{fig:chapter3:da}(a) by observing the cache line access. Figure~\ref{fig:chapter3:da}(b) shows a different example. In this example, only 32 different elements can be accessed in the array and the size of the array is 32 bytes, which is smaller than the size of one cache line. Depending on the base address of the array, the array can be stored in one cache line or two consecutive cache lines. Therefore, such a code may still be vulnerable to side-channel vulnerabilities. However, existing tools (e.g., CacheD) use a concrete base address. Under the circumstance, those tools may miss such vulnerabilities.

\subsection{Performance}

\section{Method}
\begin{figure}
    \centering
    \includegraphics[width=.35\columnwidth]{./figures/chapter3/attack.pdf}
    \caption{A side-channel attack}\label{fig:side-channel-attack}
\end{figure}
